\section{Svelte}
\label{sec:svelte}

\subsection{Overview}
\label{subsec:svelte:overview}

Svelte, created by Rich Harris and maintained by the open-source community with support from Vercel \cite{vercel:welcomes_rich}, stands out for its compiled approach, speed, and simplicity, removing the need for boilerplate code. This framework has seen significant adoption, including in enterprise settings, and has developed a large and vibrant ecosystem.

Components in Svelte are contained within a custom file type that is both readable and accessible, even for beginners. This file type is compiled into \acrshort{js}, \acrshort{html}, and \acrshort{css}, ensuring efficient and optimized performance. Unlike many other frameworks, Svelte does not use the \acrshort{vdom}, thereby avoiding its associated drawbacks. Additionally, Svelte automatically scopes styles, simplifying the management of component-specific styles and reducing the risk of style conflicts.

Svelte's popularity is reflected in its acclaim, having been voted the most loved and admired \acrshort{js} framework in the Stack Overflow survey \cite{stackoverflow:survey_2023}. Besides its technical strengths, Svelte offers an in-depth interactive walkthrough and excellent documentation, making it accessible to developers of all skill levels and easing the learning curve. Moreover, Svelte includes an SSR extension that offers numerous out-of-the-box features for full-stack development and emphasizes accessibility by providing linter warnings.

\subsubsection{Challenges and Considerations}
\label{subsec:svelte:challenges}

Due to its anti-boilerplate philosophy, Svelte presents some challenges when writing advanced state manipulation logic. However, this issue is addressed in Svelte 5 with the introduction of Runes \textit{(Svelte 5 is, at the time of writing, not yet released nor does it have a planned release date)}. Using Svelte without its supported \acrshort{ssr} extension, called SvelteKit, can feel immature.

\subsection{Strengths}
\label{subsec:svelte:strengths}
\begin{itemize}
    \item officially supported \acrshort{ssr} solution \textit{(SvelteKit)}
    \item custom file type which is easily readable and understandable
    \item great documentation with interactive walkthrough
    \item lots of usage including in enterprises
    \item big ecosystem
    \item compile time optimizations
    \item style is automatically scoped and can be bypassed using the \say{:global} selector
    \item backed by Vercel
    \item most loved/admired \acrshort{js} \gls{framework} according to the Stack Overflow survey \cite{stackoverflow:survey_2023}
    \item emphasizes accessibility using linter warnings
\end{itemize}

\subsection{Weaknesses}
\label{subsec:svelte:weaknesses}
\begin{itemize}
    \item anti boilerplate mindset can make state management more complex than needed \textit{(resolved in Svelte 5)}
    \item usage without SvelteKit doesn't feel mature
\end{itemize}

\subsection{Scores}
\label{subsec:svelte:scores}

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Method}            & \textbf{Score}                                    \\
        \hline
        Easiness/speed to learn    & 1                                                 \\ \hline
        State management           & 0.5                                               \\ \hline
        Boilerplate                & 1 \textit{(components: 1, state management: 1)}   \\ \hline
        \acrshort{api} integration & 0 \textit{(default browser fetch \acrshort{api})} \\ \hline
    \end{tabular}
    \caption{complexity}
    \label{tab:svelte:complexity}
\end{table}

\begin{table}[H]
    \centering
    \resizebox{\columnwidth}{!}{
        \begin{tabular}{|l|l|}
            \hline
            \textbf{Method}                          & \textbf{Score}                                                                                             \\
            \hline
            Community                                & 0.7 \textit{(\autoref{tab:metrics:community})}                                                             \\ \hline
            Professional Support                     & 1                                                                                                          \\ \hline
            Documentation (interactive walkthrough?) & 1                                                                                                          \\ \hline
            Ecosystem                                & 0.565 \textit{(quality: 0.83, size: 0.3; \autoref{tab:metrics:svelte:ratings} \autoref{tab:metrics:size})} \\ \hline
            Usage by other enterprises               & 1                                                                                                          \\ \hline
            Complexity                               & 0.625 \textit{(\autoref{tab:svelte:complexity})}                                                           \\ \hline
            Server Side Rendered (SSR)               & 1                                                                                                          \\ \hline
        \end{tabular}
    }
    \caption{Svelte general scores}
    \label{tab:svelte:scores}
\end{table}