\chapter{Conclusion}

This study examined various methods for building web applications, evaluating their strengths and weaknesses to identify the most suitable solution for different types of projects. The usability of each solution was also tested to provide a comprehensive evaluation.

\section{Summary of Findings}

The research indicates that Svelte, Vue, Angular, and React are top choices for general use, with each solution offering unique advantages.

\begin{enumerate}
    \item Svelte scored the highest overall, being straightforward to use for simple applications but requiring improvements in state management for more complex projects.
    \item Vue is particularly suitable for non-\acrshort{ssr} applications and offers a seamless \acrshort{dx}.
    \item React has the largest ecosystem and community support, making it versatile for various projects.
    \item Angular offers a unique features but lags behind its competitors in \acrshort{dx}.
    \item Lit excels in cross-solution components and enhancing plain \acrshort{html} sites.
    \item Hilla introduces a novel frontend-backend communication concept and could pair well with React if current issues are resolved.
\end{enumerate}

\section{Concluding Scores}

The tables provide a quick summary of the ratings for each web solution with the best score highlighted in bold.

\subsection{General Complexity}

The sources for each complexity score are derived from the following tables: \autoref{tab:angular:complexity}, \autoref{tab:lit:complexity}, \autoref{tab:react:complexity}, \autoref{tab:hilla:complexity}, \autoref{tab:svelte:complexity}, \autoref{tab:vue:complexity}

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        \textbf{Method}            & Angular      & Lit  & React      & Hilla        & Svelte     & Vue        \\
        \hline
        Easiness/speed to learn    & 0.5          & 0.5  & \textbf{1} & \textbf{1}   & \textbf{1} & \textbf{1} \\ \hline
        State management           & 0            & 0.5  & 0.5        & -            & 0.5        & \textbf{1} \\ \hline
        Boilerplate                & 0            & 0.75 & 0.5        & 0.5          & \textbf{1} & \textbf{1} \\ \hline
        \acrshort{api} integration & \textbf{0.5} & 0    & 0          & \textbf{0.5} & 0          & 0          \\ \hline
    \end{tabular}
    \caption{General complexity overview}
    \label{tab:conclusion:complexity}
\end{table}

\subsection{General Scores}

The sources for each general score are derived from the following tables: \autoref{tab:angular:scores}, \autoref{tab:lit:scores}, \autoref{tab:react:scores}, \autoref{tab:hilla:scores}, \autoref{tab:svelte:scores}, \autoref{tab:vue:scores}

\begin{table}[H]
    \centering
    \resizebox{\columnwidth}{!}{
        \begin{tabular}{|l|l|l|l|l|l|l|}
            \hline
            \textbf{Method}                          & Angular    & Lit        & React         & Hilla      & Svelte         & Vue           \\
            \hline
            Community                                & 0.6        & 0.3        & \textbf{1}    & 0.3        & 0.7            & 0.8           \\ \hline
            Professional Support                     & \textbf{1} & 0          & \textbf{1}    & \textbf{1} & \textbf{1}     & \textbf{1}    \\ \hline
            Documentation (interactive walkthrough?) & \textbf{1} & \textbf{1} & 0.5           & 0.5        & \textbf{1}     & \textbf{1}    \\ \hline
            Ecosystem                                & 0.81       & 0.465      & \textbf{0.94} & 0.115      & 0.565          & 0.775         \\ \hline
            Usage by other enterprises               & \textbf{1} & 0.5        & \textbf{1}    & 0.5        & \textbf{1}     & \textbf{1}    \\ \hline
            Complexity                               & 0.25       & 0.44       & 0.5           & 0.666\dots & 0.625          & \textbf{0.75} \\ \hline
            Server Side Rendered (SSR)               & \textbf{1} & 0.5        & 0.5           & -          & \textbf{1}     & 0.5           \\ \hline
            General Score                            & 0.809      & 0.458      & 0.777         & 0.514      & \textbf{0.841} & 0.832         \\ \hline
        \end{tabular}
    }
    \caption{General scores overview}
    \label{tab:conclusion:scores}
\end{table}

\section{Limitations}

This study focused on popular web solutions and general use cases. The rapidly evolving web development landscape means that new features could change the current standings soon. Additionally, \acrshort{dx} can be subjective and may vary among individuals and teams.

\section{Future Research}

Future research should explore the long-term performance and scalability of these solutions in different environments. Investigating the impact of new features and updates on usability and efficiency would be beneficial. A deeper analysis of specific use cases, such as e-commerce or content management systems, could provide more targeted recommendations.

\section{Concluding Remarks}

Selecting a web development solution should consider the specific needs and goals of the project. By understanding the specific advantages and limitations of each solution developers can make informed decisions that enhance their development experience. This study highlights the importance of continuous evaluation and adaptation in the fast-paced field of web development.