\tocchapter{Foreword}

As I reflect on the culmination of my internship at H.Essers and the journey towards completing this dissertation, I am filled with a profound sense of accomplishment and gratitude. Throughout my internship, I had the privilege to explore the dynamic world of next-generation web solutions, delving into innovative technologies and strategies aimed at enhancing the digital landscape.

The inspiration for this dissertation stemmed from my fascination with the ever-evolving nature of web technologies and their profound impact on developers, businesses, and society. Guided by H.Essers' vision as a frontrunner in logistics and transport solutions, I embarked on a journey to investigate how next-generation web solutions could revolutionize the industry, optimizing processes and enhancing efficiency.

I extend my heartfelt gratitude to my mentor, Tom Stijnen, and colleagues at H.Essers, whose expertise and guidance were invaluable in shaping the direction of this research. I would like to specifically thank Aaron Lardenoije for providing me with great insights and assisting me when I was stuck.

Furthermore, I am indebted to Gert Bervoets and Thierry De Block for granting me the opportunity to undertake this internship, and to the entire team at H.Essers for their unwavering support and collaboration. The collaborative environment within the organization fueled my curiosity, enabling me to engage in meaningful discussions, exchange ideas, and leverage collective expertise.

This dissertation would not have been possible without the support of my academic advisor, Mattias De Wael, who helped me refine my work.

As I conclude this journey, I am confident that the findings presented in this dissertation will contribute to the ongoing discourse surrounding next-generation web solutions, particularly in non-SSR environments. It is my hope that this research will serve as a catalyst for further innovation and inspire future endeavors in the field.

I am deeply grateful for the opportunity to undertake this research and for the invaluable experiences gained during my internship at H.Essers. I extend my sincere appreciation to everyone who has supported and contributed to this endeavor.

Thank you for your interest in this dissertation. I hope the insights presented herein will inspire continued exploration and innovation in the realm of next-generation web solutions.

\vspace{2em}

Arthur De Witte

24/05/2024





